\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-01-02 Latex/paper.tex
# new example HW cms

\subsection{CMSs}
We will define the swap rate from $T_a$ to $T_b$ at time $t$
\begin{equation*}
S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
\end{equation*}
where
\begin{align*}
01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
\end{align*}
The same way, let us define
\begin{equation*}
S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
\end{equation*}
We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$. Therefore
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \neq S_{a,b}(0).
\end{equation*}
Then convexity adjustment for a CMS will be define as
\begin{equation}
CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
\end{equation} 
Now, after some changes of measure, it is easy to show that
\begin{equation}\label{expected_t_p_cms}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{equation}
where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $S_{a,b}(T_a)$ and $M(T_a,T_p)$ we get
\begin{align} \label{clark_ocone_swap_m}
S_{a,b}(T_a) &= S_{a,b}(0) + \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s S_{a,b}(T_a) \right) dW^{01}_s  \nonumber \\
M(T_a,T_p) &= M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
\end{align}
Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
\begin{align}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \mathbb{E}^{01}_{s}\left(\partial_x S_{a,b}(T_a)  D_s x_{T_a} \right)
\mathbb{E}^{01}_{s}\left(\partial_x M(T_a,T_p)  D_s x_{T_a} \right) ds \right) \nonumber \\
&= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0)\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a}  \left(\mathbb{E}^{01}\left(D_s x_{T_a}\right)\right)^{2}
 ds\right) \nonumber \\
&+ \cdots
\end{align}

\begin{example}
In the case of a Hull-White model, we showed  in 
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
and therefore, we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}^{01}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
\end{equation*}

>>>>

\subsection{CMSs}
We will define the swap rate from $T_a$ to $T_b$ at time $t$
\begin{equation*}
S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
\end{equation*}
where
\begin{align*}
01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
\end{align*}
The same way, let us define
\begin{equation*}
S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
\end{equation*}
We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$. Therefore
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \neq S_{a,b}(0).
\end{equation*}
Then convexity adjustment for a CMS will be define as
\begin{equation}
CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
\end{equation} 
Now, after some changes of measure, it is easy to show that
\begin{equation}\label{expected_t_p_cms}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{equation}
where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
\begin{equation} \label{clark_ocone_swap_m}
M(T_a,T_p) = M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
\end{equation}
Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
\begin{align}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
&=  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right)
\end{align}

\begin{example}
In order to get a little bit of intuition we will use the las t expression for the particular case of a Hull-White model. In this case, is easy to show that 
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
therefore we have that 
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2}  \mathbb{E}^{0,1}_s\left(\partial_x S_{a,b}(s) \partial_x M(s,T_p)  \right) ds \right)
\end{equation*}
Now, if we apply again Clark-Ocone to $\partial_x M(s,T_p)$, we get that

\begin{align*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} ds \right) \\
&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\partial_x S_{a,b}(s) \int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s} \partial^{2}_{x} S_{a,b}(u_1) \partial^{2}_{x} M(u_1,T_p) (D_{u_1}x_s)^{2}  du_1 ds \right)
\end{align*}
We must observe that, if we repeat the same argument and
